### 2017-01-18 robust-software.tex

How to write high quality documentation has been described elsewhere~\cite{karimzadeh2016}
and so here we only cover two minimal types: the README and usage. 
The README is usually available even before the software is installed, 
and exists
to get a new user started and point them towards more
help. Usage is a terse, informative command-line help message that
guides the user in the correct use of the software.

Numerous guidelines exist on how to \ruleminor{write a good
README file}~\cite{Johnson1997,gnustandards}.
Some key common features are listed below.

@@

Almost all command-line applications use a combination of
POSIX~\cite{posix2016} and GNU~\cite{gnustandards} standards for usage. 
More standard command-line behaviours are detailed in \cite{Seemann2013}.
The key features of a usage message include:

@@

Usage should be 
printed to standard output so that it can be 
combined with other bash utilities like \texttt{grep},
and it should finish with an appropiate exit code
depending upon whether it is a response to an error,
or was explicitly requested.

>>>>

How to write high quality documentation has been described elsewhere~\cite{karimzadeh2016}
and so here we only cover two minimal types: the README and usage. 
The README is usually available even before the software is installed, 
exists
to get a new user started, and points them towards more
help. Usage is a terse, informative command-line help message that
guides the user in the correct use of the software.

Numerous guidelines exist on how to \ruleminor{write a good
README file}~\cite{Johnson1997,gnustandards}. 
At a minimum, your README should:

@@

Almost all command-line applications use a combination of
POSIX~\cite{posix2016} and GNU~\cite{gnustandards} standards for usage. 
More standard command-line behaviours are detailed in \cite{Seemann2013}.
Your software's usage should:

@@

Usage should be 
printed to standard output so that it can be 
combined with other bash utilities like \texttt{grep},
and it should finish with an appropiate exit code.
